% Created 2012-06-18 Mon 20:35
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\providecommand{\alert}[1]{\textbf{#1}}

\title{}
\author{Neil Smithline}
\date{\today}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs Org-mode version 7.7}}

\begin{document}





\begin{center}


\end{center}

\section*{Objective}
\label{sec-1}

I am looking to add my experience and creativity to an exciting engineering team be part of a fast-paced, cutting-edge technology company.
\section*{General Skills}
\label{sec-2}

\begin{itemize}
\item Familiar with a wide variety of development processes including Waterfall, eXtreme Programming (XP), Agile Software Development, Unified Rational Development, etc\ldots{}
\item Self-motivated starter.
\item Happy to adapt to new technology areas, utilize different development processes, and perform within a multitude of organizational structures.
\item Extensive experience interacting with a wide-range of domestic and international companies, in a diverse set of industries, varying in size from startups to \href{http://www.forbes.com/global2000/list/}{Global 2000 Companies}.
\item Comfortable working alone or as a member of a team, locally or remotely, as a technical lead or individual contributor.
\end{itemize}
\section*{Significant Technical Accomplishments}
\label{sec-3}

\begin{itemize}
\item Enterprise architect: architected and cowrote WLS security framework\footnote{Architected \href{http://bit.ly/AF3TMb}{WebLogic Server security framework}. January 2012 marks the 11$^{\mathrm{th}}$ year that it will be the foundation of security for \href{http://bit.ly/z23Zss }{BEA's WebLogic Server} (now \href{http://bit.ly/AF3TMb) }{Oracle's Fusion Middleware}) and other \href{http://en.wikipedia.org/wiki/Middleware}{middleware} products. }.
\item Object oriented design and analysis experience including use of \href{http://en.wikipedia.org/wiki/Rational_rose}{Rational Rose} and \href{http://en.wikipedia.org/wiki/Borland_Together}{TogetherJ/Borland Together}.
\item Application security expert including knowledge of Java security (\href{http://en.wikipedia.org/wiki/J2ee}{JEE/J2EE} and \href{http://en.wikipedia.org/wiki/J2ee}{JSE/J2SE}), identity management (\href{http://en.wikipedia.org/wiki/Idm}{IDM}), web services security, \href{http://en.wikipedia.org/wiki/SAML}{SAML}, \href{http://en.wikipedia.org/wiki/XACML}{XACML}, \href{http://en.wikipedia.org/wiki/Kerberos_(protocol)}{Kerberos}, Firewalls, \href{http://en.wikipedia.org/wiki/DMZ_(computing)}{DMZs}, and many other technologies. Familiar with many national and international security guidelines including \href{http://en.wikipedia.org/wiki/Common_criteria}{Common Criteria}, Swiss and German Banking laws, security practices of dozens of the world's most secure companies and government agencies.
\item Intimately familiar with the concepts behind application servers: \href{http://en.wikipedia.org/wiki/Oracle_WebLogic_Server}{WebLogic Server} expert, \href{http://en.wikipedia.org/wiki/Websphere}{WebSphere}, and \href{http://en.wikipedia.org/wiki/Jrun}{JRun} experience.
\item Extensive experience with a variety of programming languages and operating systems.
\end{itemize}
\section*{Employment}
\label{sec-4}
\subsection*{Open Source Developer/Personal Leave, January 2011-Present}
\label{sec-4-1}
\subsection*{Security Contractor/Consultant (Newton, MA), June 2008-December 2011}
\label{sec-4-2}
\subsection*{BEA Systems (Boston, MA), October 1999-May 2008}
\label{sec-4-3}
\subsubsection*{Chief Security Architect, November 2000-May 2008}
\label{sec-4-3-1}

\begin{itemize}
\item Responsible for all aspects of security in all of BEA’s products including tracking of relevant standards, and long-term security direction.
\item Co-architected the BEA WebLogic Server security infrastructure which has been adopted by all BEA products and, following the BEA/Oracle buyout, is being adopted by Oracle products (eg: \href{http://docs.oracle.com/cd/E21764_01/web.1111/b32511/intro_ws.htm#autoId0}{Oracle Web Services Manager}).
\item Implemented major portions of the security system including Java 2 Security integration.
\item Developed security coding standards and processes used throughout BEA, created educational material and toured many of BEA's sites to educate (and learn from) the developers.
\item Created and managed BEA's vulnerability process and team. Growing it from two two people and two vulnerabilities a year to 50+ vulnerabilities a year with a company-wide team consisting of developers, management, project and product management, QA, technical publications, legal.
\item Worked hand-in-hand with key customers to help them design an effective security architecture using both BEA and non-BEA products.
\item Orchestrated all technical interactions with third party security vendors and helped them design their integration strategies with the WebLogic Server's security system.
\item Helped key customers design and implement an effective security architecture.
\end{itemize}
\subsection*{Bowne Internet Solutions (Cambridge, MA)}
\label{sec-4-4}
\subsection*{Kronos Incorporated (Waltham, MA)}
\label{sec-4-5}
\subsection*{Remedy Corporation (Mountain View, CA)}
\label{sec-4-6}
\subsection*{Sun Microsystems (Palo Alto, CA)}
\label{sec-4-7}
\subsection*{Kodak Research Laboratories, Eastman Kodak (Rochester, NY)}
\label{sec-4-8}
\subsection*{Computer Science Department, University of Rochester}
\label{sec-4-9}
\subsection*{Computer Science Department, University of Buffalo}
\label{sec-4-10}
\subsection*{Grumman Aerospace Systems}
\label{sec-4-11}
\section*{Education}
\label{sec-5}

\begin{itemize}
\item Ph.D. all but dissertation, Computer Science, September 1986-1990; University of Rochester.
\item M.S., Computer Science, May 1989; University of Rochester.
\item B.S. with honors, Computer Science, May 1987; University of Buffalo
\item University of Buffalo's President's List (4.0/4.0 GPA), Fall 1984 and Spring 1985
\item University of Buffalo's Dean's List (3.6/4.0 GPA), Fall 1986 and Fall 1987
\item New York State Regent's Scholarship Fall 1983
\item National Merit Letter of Commendation Spring 1982
\end{itemize}

\end{document}